Programming Distributed Control Planes

### 2016-01-19 paper/propane.tex
Example 2 in paper. Better rule compression for memory reduction.

\example{1}

\example{2}

@@

Finally, we can combine these constraints logically to specify the network-wide policy.

@@

% correct by construction
% mention centralized
% mention attributes

>>>>

\para{Example 1}

We now show how to write the routing policy for the backbone network in Section~\ref{sec:motivation}.

\para{Example 2}

@@

Finally, we can combine these constraints logically to specify the network-wide policy:

@@

Once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. Similarly, it can check for aggregate-induced black holes up to $k$ failures.
